\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\title{Progress\_ITP25\_B3\_W57.pdf}
\author{Extracted from PDF}
\date{\today}

\begin{document}
\maketitle

\section*{Page 1}
1 | P a g e 
 
Sri Lanka Institute of Information Technology 
 
 
 
 
 
 
 
SMARTBIN 
Assignment 2 – 70\% Progress Report 
Group ID :  ITP25\_B3\_WC57 
IT Number  Student Name  Student e-mail Address  Student Contact 
Number  
IT23373952  
  
Dissanayake D.S.  it23373952@my.sliit.lk  0719296379  
  
IT23232990  
  
Thennakoon S.S.H.  
  
it23232990@my.sliit.lk  
  
0786421227  
IT23380950  Perera M.K.P .T.S.  
  
it23380950@my.sliit.lk  0784536072  
IT23325814   Weerathunga A.W.T.C  
  
it23325814@my.sliit.lk  
  
0755359114  
  
IT23367562  
  
Lakshitha W. G. D.  
  
it23367562@my.sliit.lk  0763804351  
 
 


\section*{Page 2}
2 | P a g e 
 
Contents 
1. Progress ................................ ................................ ................................ ............... 4 
2. User Stories ................................ ................................ ................................ .......... 6 
3. ER Diagram ................................ ................................ ................................ ......... 11 
4. Normalized Schema ................................ ................................ ............................  11 
5. System Architecture ................................ ................................ ............................  13 
6. Innovation................................ ................................ ................................ ........... 13 
7.Commercialization ................................ ................................ ................................ .. 14 
8.Test Cases................................ ................................ ................................ ............... 15 
Financial management  | Thennakoon S.S.H.| IT23232990 ................................ .......... 16 
User , Staff  and Complaints management | Dissanayake D.S. IT23373952 ..................  17 
Recycling Management |  Perera M K P T S ................................ ................................ . 20 
IT23380950 ................................ ................................ ................................ ............ 20 
Schedule/ Resources Management | Lakshitha W G D IT23367562 .............................  22 
Pickup Request Management | ................................ ................................ ................. 25 
9.Functions  1.User/Staff Management ................................ ................................ ........ 27 
Database Schema ................................ ................................ ...............................  29 
Database Operations ................................ ................................ ...........................  36 
Algorithms ................................ ................................ ................................ .......... 39 
Pseudocode ................................ ................................ ................................ ........ 39 
Flow Chart (Activity Diagram) ................................ ................................ ............... 44 
2. Financial Management ................................ ................................ ........................  46 
Database Schema ................................ ................................ ...............................  47 
Algorithms ................................ ................................ ................................ .......... 50 
Pseudocode ................................ ................................ ................................ ........ 51 
Flow chart(Activity Diagram) ................................ ................................ ................. 55 
3. Recycling Management ................................ ................................ ........................  57 
4.Schedule/ Resource Management ................................ ................................ ......... 70 
Database Schema ................................ ................................ ...............................  72 

\section*{Page 3}
3 | P a g e 
 
Algorithms ................................ ................................ ................................ .......... 76 
Pseudocode ................................ ................................ ................................ ........ 79 
7. Pickup Request Management ................................ ................................ ............ 83 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 

\section*{Page 4}
4 | P a g e 
 
 
1. Progress 
 
High level user story/ function Completed 
(Y/N, 
comment) 
Responsible 
member (Name) 
User/ Staff Login Yes Dissanayake D.S. 
   
   
Subscription Plan Management Yes Thennakoon 
S.S.H. 
Creating Salary Plans Yes Thennakoon 
S.S.H. 
Budget Allocation  No  Thennakoon 
S.S.H. 
Pricing Page No, Currently 
working on it 
Thennakoon S.S. 
H. 
Payment Notification System No Thennakoon 
S.S.H. 
Pickup Request Form with Validations (User Side) Yes Weerathunga 
A.W.T.C 
“My Bin Details” Page and “Pickup Request Details” 
Page with CRUD Operations (User Side) 
Yes Weerathunga 
A.W.T.C 
 
Advanced Search Functionality (Both User and 
Admin Side) 
Yes Weerathunga 
A.W.T.C 
 
Pickup Requests and Pickup Request Details Pages 
with Read, Update and Delete (Admin Side) 
Yes Weerathunga 
A.W.T.C 
 
Status Management for Pickup Request (Admin 
Side) 
Yes Weerathunga 
A.W.T.C 
 
Auto Generated Emails (Admin Side) No, currently 
working on it 
Weerathunga 
A.W.T.C 
 
Payment Portal No Weerathunga 
A.W.T.C 
 

\section*{Page 5}
5 | P a g e 
 
Report Generation and Download Report About 
Completed Pickup Requests (Admin Side) 
No Weerathunga 
A.W.T.C 
 
   
Schedule Home page with navigation (Admin Side) Yes Lakshitha W G D 
Schedule management page with form validation 
and Displaying current adding schedules with CRUD 
Yes Lakshitha W G D 
 
Truck management page with form validation and 
Displaying current adding Trucks  with CRUD  
 
Yes Lakshitha W G D 
 
Tool management page with form validation and 
Displaying current adding Tools with CRUD 
 
Yes Lakshitha W G D 
 
Equipment management page with form validation 
and Displaying current adding Equipment with 
CRUD 
 
Yes Lakshitha W G D 
 
Schedule display page with Search Functionality Yes Lakshitha W G D 
 
Resources display page with Search Functionality 
 
Yes Lakshitha W G D 
 
Tracking current truck  location function No, currently 
working on it 
 
Lakshitha W G D 
 
Schedule email generate function No Lakshitha W G D 
 
Recycle Request Form with Validations (User Side) 
 
Yes Perera M K P T S 
 
“My Orders” Page and “My Order Details” Page with 
CRUD Operations (User Side) 
 
Yes 
 
Perera M K P T S 
 
Recycling Requests and Recycling Order Details 
Pages with Read, Update and Delete (Admin Side) 
 
Yes Perera M K P T S 
 
Status Management (Approved, Rejected) for 
Recycling Request (Admin Side) 
 
Yes Perera M K P T S 
 
Advanced Search Functionality 
 
Yes Perera M K P T S 
 
Auto Generated Emails (Admin Side) 
 
No, currently 
working on it 
 
Perera M K P T S 
 
Payment Portal No Perera M K P T S 

\section*{Page 6}
6 | P a g e 
 
  
 
 
 
 
 
 
 
 
 
Repository 
https://github.com/DinithaSasinduDissanayake/SmartBin 
 
 
 
 
 
 
 
2. User Stories 
 
  Function  User Story  
 
User/Staff 
Management 
As a customer, I want to register securely using my email and 
password, so that I can access SmartBin services.  
As a user (customer/staff/admin), I want to log in securely using 
my credentials.  
As a user (customer/staff/admin), I want the option to enable 
Multi-Factor Authentication (MFA) for enhanced login security.  

\section*{Page 7}
7 | P a g e 
 
As a customer, I want to manage my profile (name, contact, 
primary service location).  
As an administrator, I want basic role management (Admin, Staff, 
Customer) to control access.  
As a staff member, I want to view my assigned tasks/schedule for 
the day.  
As an administrator/manager, I want to manage detailed staff 
profiles including skills, performance notes, and uploaded 
verification documents.  
As an administrator/manager, I want the system to track staff 
attendance digitally (e.g., clock-in/out).  
As an administrator/manager, I want to monitor staff performance 
against defined Key Performance Indicators (KPIs).  
As a user, I want a password recovery option via email, so that I can 
regain access if I forget my password.  
As an administrator, I want to view a list of all registered users and 
staff.  
As a customer, I want to add multiple service locations to my 
profile.  
As an administrator/manager, I want to view comprehensive staff 
activity logs and performance summaries to monitor work.  
As a user (customer/staff), I want to submit a complaint or provide 
feedback through a dedicated form in the system.  
As an administrator/manager, I want to view, track, assign, and 
update the status of submitted complaints/feedback.  
As an administrator/manager, I want the system to support 
escalation rules/notifications for unresolved complaints based on 
priority/time.  
 
 
 
  Function  User Story  
 
Financial 
Management 
As a customer, I want to view my current subscription plan and 
basic billing details.  
As a financial manager, I want to define and manage flexible 
subscription plans (e.g., Residential, Commercial), including 
handling upgrades/downgrades with prorated billing.  
As a financial manager/admin, I want a real-time financial 
dashboard displaying key KPIs (e.g., revenue, expenses, 
subscriptions, payments).  

\section*{Page 8}
8 | P a g e 
 
As a financial manager, I want the system to process payroll 
accurately, calculating salaries, standard deductions, taxes, and 
incorporating approved bonuses/incentives.  
As a financial manager, I want the system to generate 
downloadable payslips for staff based on processed payroll data.  
As a customer, I want to receive simple notifications for 
upcoming/due payments.  
As a financial manager, I want to record payments made against 
customer accounts.  
As a customer, I want to view my payment history.  
As a financial manager, I want basic integration with a payment 
gateway for online payments.  
As a financial manager, I want to generate comprehensive financial 
reports (including income, expenses, segmented revenue, and 
basic tax summaries).  
As a staff member, I want to view my detailed pay slip generated by 
the system.  
 
  
 
  Function  User Story  
 
Recycling 
Management 
As a recycling partner, I want to register my company profile, so 
that I can participate in purchasing garbage for recycling purposes.  
As an admin, I want to list available garbage for sale so that users 
can browse and purchase it for recycling.  
As an admin, I want to approve or reject purchase requests for 
garbage so that I can control the sales process.  
As a recycling partner, I want to submit a purchase request for 
garbage so that I can buy it for recycling purposes.  
As an admin, I want to categorize garbage types (e.g., plastic, 
paper) so that users can easily find what they need for recycling.  
As a user, I want to receive confirmation of my purchase request so 
that I know it’s being processed.  
As an admin, I want to generate a report of garbage sold so that I 
can analyze sales trends.  
 
 
  Function  User Story  

\section*{Page 9}
9 | P a g e 
 
 
Schedule / Resource 
Management 
 As an admin/scheduler, I want to create basic collection routes 
manually assigning areas/customers, so that I can efficiently 
organize garbage collection schedules.  
  
As a driver (staff), I want to view my assigned route and customer 
list for the day, so that I can plan my garbage collection activities.  
  
As an admin, I want to register vehicles and assign basic status 
(Active, Maintenance), so that I can effectively oversee the 
garbage collection fleet.  
  
As a driver (staff), I want to mark pickups as completed on my 
route list, so that I can keep track of my progress during garbage 
collection.  
  
As an admin, I want a map view showing basic vehicle locations, so 
that I can monitor the progress of garbage collection routes.  
  
As an admin, I want to add new equipment and tools then, so that 
I can manage the availability of tools.  
 
 
 
  Function  User Story  
 
Pickup Request 
Management 
As a customer, I want to submit a garbage pickup request by 
providing my name, contact, email, community, waste type, service 
type, preferred date, address and location so that I can schedule 
waste collection.  
As a customer, I want to be notified when my pickup request is 
approved, on progress or rejected so that I stay informed.  
As an admin/scheduler, I want to view all pickup requests 
submitted by customers so that I can review and approve or reject 
them.  
As an admin/scheduler, I want to update the status of pickup 
requests (pending, approved, on progress, completed, rejected) so 
that customers can track their requests.  
As a customer, I want to receive a confirmation email when my 
pickup is scheduled so that I can pay for the pickup.  
As a customer, I want to delete my submitted pickup request 
before approval so that I can cancel the request if needed.  

\section*{Page 10}
10 | P a g e 
 
As a customer, I want to search my pickup requests, so that I can 
find specific requests easily.  
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 

\section*{Page 11}
11 | P a g e 
 
3. ER Diagram 
 
  Figure 01: ER Diagram of the “SmartBin” Garbage Management System 
 
 
 
Link to : 
https://app.diagrams.net/\#G1L4Tjhdxgdzd8MA14IGwOoYATRYkJrpY3\#\%7B\%22pageId\%22
\%3A\%22D7q4ME-1\_\_F6XudRjVuN\%22\%7D 
 
 
 
 
4. Normalized Schema 
 
 


\section*{Page 12}
12 | P a g e 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
  Figure 02: Relational Schema for “SmartBin” Garbage Management System 
 


\section*{Page 13}
13 | P a g e 
 
 
5. System Architecture 
 
Figure 03: “SmartBin” Management System Architecture 
 
 
 
 
6. Innovation 
 
1. Smart Waste Collection Optimization –  
      Use GPS and AI to optimize the garbage collecting routes by reducing the time, 
Energy and fuel. 
2. Integrated Financial Management System –  


\section*{Page 14}
14 | P a g e 
 
     Customers can subscribe to different subscription plans through pricing page as 
their choice and receive their invoice to their dashboard.   The System tracks how the 
funds are collected and allocated for expenses like salaries, fuels, and maintenance. 
3. Advance User and Staff Management –  
       Each Customer or Staff member have their own dashboard, which they can 
access securely by using their own credentials.  The system uses digital attendants 
tracking system to track the attendants of each staff member. Staff tasks are assigned 
dynamically by considering the availability, workload and past performances. 
  
4. Waste Selling place for Recyclers 
                     Recycles can place their orders for the waste can be done directly by the System.     
Track the market pricing for each waste type and ensure fair pricing 
 
5. Smart Complaint System – 
         Customers and Staff Members can easily submit their Complaints through the 
dedication form in their dashboard.  Administrator receives those submitting 
complaints instancy and can give the reasonings or solutions directly through the 
system. 
 
 
 
 
 7.Commercialization 
  
     The “SmartBin’ Garbage Management System have different commercialization 
strategies that make the system is unique among the other systems. 
 Our System has different Subscription plans for waste collection that make by considering 
the customers’ needs with flexible pricing. Them gave Special plans for business and large-
scale waste producers with custom pricing.  

\section*{Page 15}
15 | P a g e 
 
We sell segregated recycling materials like plastics, paper, Matel for recyclers for additional 
income.  After some period, we plan to allow the ecofriendly brands to advertising on the 
“SmartBin” website. Also offer sponsorship opportunities on waste bins and waste 
collection vehicles for sustainable brands. 
 
The “SmartBin” seek grands and fundings from environmental agencies for sustainable 
waste Management. Partner with local government to implement “SmartBin” in public 
waste Management system 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
8.Test Cases 
 

\section*{Page 16}
16 | P a g e 
 
Financial management  | Thennakoon S.S.H.| IT23232990 
 
 
Test ID Test Case Preconditions Steps Expected Result 
TC\_SUB\_01 Creation of a 
new 
subscription 
plan 
The Financial 
Manager is 
logged in 
First, go to the Plans 
section. Click the 
"Add New" button. 
Then complete the 
form. Submit. 
A success message 
appears and the new 
plan is visible. 
TC\_SUB\_02 Stop a 
duplicate plan 
name 
A plan named 
"Basic" already 
exists 
First, go to Plans. 
Click "Add New" . 
Then set the Name 
field to "Basic" . 
Finally, submit. 
An error message 
appears and the new 
plan is not created. 
TC\_SUB\_03 Subscription 
plan update 
Plan "Basic" 
exists 
First, find "Basic" . 
Next, click "Update" . 
Then change the 
price. Submit. 
A success message 
appears and the price 
is updated. 
TC\_SAL\_01 Salary package 
creation 
The Financial 
Manager is 
logged in 
First, go to Salary 
Plans. Click "Add 
New" . Complete the 
form, then submit. 
A success message 
appears and the new 
plan is created. 
TC\_BUD\_01 Budget 
allocation 
submission 
The financial 
manager is 
logged in 
First, go to Budget. 
Enter the expense 
details and submit. 
An entry is recorded 
without issues. 
TC\_PAY\_01 Payroll process A payroll officer 
is logged in 
First, select 
employees. Next, 
run payroll. Finally, 
confirm. 
Payments are 
processed and the 
records are updated. 

\section*{Page 17}
17 | P a g e 
 
 
 
User , Staff  and Complaints management | Dissanayake D.S. 
IT23373952 
 
Test ID Test Case 
Description 
Preconditio
ns 
Steps Expected 
Result 
TC\_REG
\_01 
Confirm 
successful user 
registration with 
valid 
information 
None 1. Go to registration page. 2. Fill all required 
fields with valid information. 3. Form 
submission. 
User account 
created. 
Redirect to 
login or 
success 
message 
shown. 
TC\_REG
\_02 
Verify 
registration 
failure with 
invalid email 
None 1. Navigate to registration page. 2. Populate 
fields with invalid email format. 3. Form 
submission. 
Invalid email 
error message 
appears. User 
not registered. 

\section*{Page 18}
18 | P a g e 
 
TC\_REG
\_03 
Existing email 
check 
registration 
failure 
User with 
existing 
email 
"existing@t
est.com" 
already 
exists 
1. Go to registration page. 2. Fill in fields with 
"existing@test.com" . 3. Submit form. 
Error message 
that the email 
already exists. 
User is not 
registered. 
TC\_LOG
IN\_01 
Verify 
successful login 
with valid 
credentials 
User 
account 
exists and 
is active 
1. Go to login page. 2. Fill in correct email 
and password. 3. Click Login. 
User logged in 
successfully. 
Redirected to 
correct 
dashboard. 
TC\_LOG
IN\_02 
Confirm login 
failure with 
invalid 
password 
User 
account 
exists 
1. Go to login page. 2. Enter correct email 
and incorrect password. 3. Click Login. 
Error message 
"Invalid 
credentials" is 
shown. Login 
fails. 
TC\_PRO
FILE\_01 
Verify user is 
able to view 
profile details 
User is 
logged in 
1. Go to Profile section. 2. Observe displayed 
details. 
User's name, 
email, 
contact info 
displayed 
correctly. 

\section*{Page 19}
19 | P a g e 
 
TC\_PRO
FILE\_02 
Check if user 
can edit profile 
information 
User is 
signed in 
1. Go to Profile section. 2. Click "Edit. " . 3. 
Modify a field. 4. Save changes. 
Success 
message is 
displayed. 
Profile 
displays 
updated 
information. 
TC\_CO
MP\_01 
Verify that user 
can submit a 
complaint 
User logged 
in 
1. Go to Complaint section. 2. Complete 
complaint form. 3. Submit complaint. 
Success 
message is 
displayed. 
Complaint is 
added to 
user's history. 
TC\_ATT\_
01 
Verify staff can 
clock-in 
Staff user 
logged in 
1. Navigate to Attendance section. 2. Click 
"Clock In. " 
Success 
message. 
Attendance 
record 
created with 
status 
'Present' . 
TC\_ATT\_
02 
Verify 
employees are 
able to clock-
out 
Staff user is 
clocked in 
1. Navigate to Attendance section. 2. Click 
"Clock Out. " 
Success 
message. 
Attendance 
record 
updated with 
clock-out 
time. 

\section*{Page 20}
20 | P a g e 
 
 
Recycling Management |  Perera M K P T S  
IT23380950 
Test 
ID 
Test Case 
Description 
 
Preconditions 
 
Steps 
 
Expected 
Result 
 
TC-
01 
 
Successful 
Request 
Submission 
 
Recycler is logged 
in, database is 
accessible 
 
1. Go to "Garbage Recycle" 
option 2. Fill form (e.g., 
Name: "John" , Email: 
tharu123@gmail.com, 
contact number: 
0784525365, Waste: 
"Plastic" , Qty: 10,  
Community: Household, 
Pickup Location: "25/A 
Street Rd, Gampaha, 
Preferred pickup date \& 
time: 02/05/2025 
02.50pm, Collection 
preferences: "Delivery") 
3. Click "Submit" . 
 
Payment 
amount 
displayed (e.g., 
500 if unit 
amount is 
50/kg), "Request 
submitted 
successfully" 
shown, 
redirected to My 
Order page with 
request (Status: 
"Pending"). 
 
TC-
02 
 
Incomplete 
Form 
Submission 
 
Recycler is logged 
in 
 
1. Go to "Garbage Recycle" 
option. 
2. Leave "Contact 
number" blank, fill others 
(e.g., Name: "John" , Email: 
tharu123@gmail.com,Was
te: "Plastic" , Qty: 10,  
Community: Household, 
Pickup Location: "25/A 
Street Rd, Gampaha, 
Preferred pickup date \& 
time: 02/05/2025 
02.50pm, Collection 
preferences: "Delivery") 
"Please fill in this 
field" message 
appears, form 
remains 
editable, no 
submission 
occurs. 
 
TC-
03 
 
Invalid 
Quantity 
Submission 
 
Recycler is logged 
in 
 
1. Go to "Garbage Recycle" 
option. 
2. Try to  fill form with 
invalid quantity (eg: -5) 
 
"Quantity must 
be a positive 
number" 
message 
appears, form 

\section*{Page 21}
21 | P a g e 
 
remains 
editable, no 
submission 
occurs. 
 
TC-
04 
 
View 
Submitted 
Requests 
 
Recycler is logged 
in, has a request 
(e.g., Plastic, 
10kg,  "Pending") 
Unit price of 
plastic = 50 
 
1. Go to My Order page. 
 
List shows 
request details: 
Waste Type: 
"Plastic" , 
Quntity: "10kg" , 
Amount: "500" , 
Status: 
"Pending" , with 
"Update" and 
"Delete" buttons 
visible. 
 
TC-
05 
 
Update a 
Request 
 
Recycler is logged 
in, has a request 
(e.g., Plastic, 
10kg, 500, 
"Pending") 
 
1. Go to My Order page 
2. Click "Update" 
3. Change Quantity to 
15kg. 
4. Save changes. 
 
Payment 
updates (e.g., 
750 /=if rate is 
50/kg), request 
saved with 
Status: 
"Pending" , My 
Order page 
shows updated 
details. 
 
TC-
06 
 
Delete a 
Request 
 
Recycler is logged 
in, has a request 
(e.g., Glass, 
5kg,500, 
"Pending") 
 
1. Go to My Order page. 
2. Click "Delete" . 
 
"Request 
deleted" 
message 
appears, request 
is removed from 
My Order page. 
 
TC-
07 
 
View All 
Requests as 
Admin 
 
Admin is logged 
in, two requests 
exist (e.g., 
Recycler1: 
Plastic, 10kg; 
Recycler2: Paper, 
20kg) 
 
1. Go to Recycling Request 
page. 
 
List shows all 
requests (e.g., 
Recycler1: 
Plastic, 10kg, 
500, "Pending"; 
Recycler2: 
Paper, 20kg, 
600, "Pending") 
with "Delete" 

\section*{Page 22}
22 | P a g e 
 
and "Update 
Status" buttons. 
 
TC-
08 
 
Approve a 
Request 
 
Admin is logged 
in, request exists 
(e.g., Plastic, 
10kg, 500, 
"Pending") 
 
1. Go to Recycling Request 
page. 
2. Click "Update Status" 
3. Select "Approved" . 
 
Status updates 
to "Approved" in 
database, 
recycler sees 
"Approved" on 
My Order page. 
 
TC-
09 
 
Reject a 
Request 
 
Admin is logged 
in, request exists 
(e.g., Glass, 5kg, 
500, "Pending") 
 
1. Go to Recycling Request 
page. 
2. Click "Update Status" 
3. Select "Rejected" . 
 
Status updates 
to "Rejected" in 
database, 
recycler sees 
"Rejected" on 
My Order page. 
 
TC-
10 
 
Delete a 
Request as 
Admin 
 
Admin is logged 
in, request exists 
(e.g., Paper, 
20kg,600, 
"Pending") 
 
1. Go to Recycling Request 
page. 
2. Click "Delete" . 
 
"Request 
deleted" 
message 
appears, request 
is removed from 
Recycling 
Request page 
and My Order 
page. 
 
Schedule/ Resources Management | Lakshitha W G D IT23367562 
 
Test ID Test Case 
Description 
Preconditions Steps Expected Result 
TC\_SCH\_01 
 
Confirm 
successful 
route 
creation by 
admin 
 
Admin is 
logged in with 
valid 
credentials 
 
1. Navigate to 
"Schedule 
Management" page. 
2. Fill in route details 
(areas, truck 
number, date, time). 
3. Submit form. 
Route is created 
successfully. New 
schedule appears 
in the system with 
status "Waiting" . 
 
TC\_SCH\_02 
 
 
Verify route 
creation 
Admin is 
logged in with 
1. Navigate to 
"Schedule 
Management" page. 
Error message 
appears: "Invalid 
truck number. Truck 

\section*{Page 23}
23 | P a g e 
 
failure with 
invalid truck 
 
valid 
credentials 
2. Enter invalid truck 
number (e.g., non-
existent truck). 3. 
Submit form 
not found. " Route is 
not created. 
 
TC\_SCH\_03 
 
Confirm 
driver can 
view 
assigned 
route 
 
Driver is logged 
in, route 
assigned for 
today 
1. Navigate to "My 
Routes" page. 2. 
Select current date. 
3. View route details. 
Route details 
(schedule number, 
areas, truck 
number, time, 
status) are 
displayed. 
TC\_SCH\_04 
 
Verify driver 
cannot view 
route if none 
assigned 
 
Driver is logged 
in, no route 
assigned for 
today 
 
1. Navigate to "My 
Routes" page. 2. 
Select current date. 
3. View route details. 
Message appears: 
"No route assigned 
for today. " 
 
TC\_TRK\_01 
 
Confirm 
successful 
truck 
registration 
by admin 
 
Admin is 
logged in with 
valid 
credentials 
 
1. Navigate to 
"Vehicle 
Management" page. 
2. Fill in truck details 
(truck ID, tank 
capacity, fuel). 3. 
Submit form. 
Truck is registered 
successfully. New 
truck appears with 
status "Active" and 
availability 
"Available" . 
TC\_TRK\_02 
 
Verify truck 
registration 
failure with 
duplicate ID 
 
Admin is 
logged in, truck 
ID already 
exists 
 
1. Navigate to 
"Vehicle 
Management" page. 
2. Enter existing 
truck ID. 3. Submit 
form. 
Error message 
appears: "Truck ID 
already exists. " 
Truck is not 
registered 
 
TC\_SCH\_05 
 
Confirm 
driver can 
mark 
pickups as 
completed 
 
Driver is logged 
in, route 
assigned with 
status 
"Waiting" 
 
1. Navigate to "My 
Routes" page. 2. 
Select route. 3. Mark 
specific areas as 
completed. 4. 
Submit updates. 
 
Areas are removed 
from route. If all 
areas completed, 
status updates to 
"Completed" , and 
truck availability 
changes to 
"Available" 
TC\_SCH\_06 
 
Verify 
pickup 
completion 
failure with 
invalid areas 
 
Driver is logged 
in, route 
assigned 
 
1. Navigate to "My 
Routes" page. 2. 
Select route. 3. Mark 
non-existent areas 
as completed. 4. 
Submit updates. 
Error message 
appears: "Invalid 
areas specified. " 
Route is not 
updated. 
 

\section*{Page 24}
24 | P a g e 
 
TC\_TRK\_03 
 
Confirm 
admin can 
view truck 
locations on 
map 
 
Admin is 
logged in, 
active trucks 
exist with 
location data 
 
1. Navigate to 
"Vehicle 
Management" page. 
2. Select "View Map" . 
3. View truck 
locations. 
 
Map displays all 
active trucks with 
their locations 
(latitude, longitude) 
and availability 
status 
TC\_TRK\_04 
 
Verify map 
view failure 
when no 
active 
trucks 
 
Admin is 
logged in, no 
active trucks 
exist 
 
1. Navigate to 
"Vehicle 
Management" page. 
2. Select "View Map" . 
3. View truck 
locations 
Message appears: 
"No active trucks 
available. " Map 
remains empty. 
 
TC\_EQP\_01 
 
Confirm 
successful 
equipment 
addition by 
admin 
 
Admin is 
logged in with 
valid 
credentials 
 
1. Navigate to 
"Resource 
Management" page. 
2. Select "Add 
Equipment" . 3. Fill in 
details (equipment 
ID, name). 4. Submit 
form. 
Equipment is 
added successfully. 
New equipment 
appears with status 
"Operational" 
 
TC\_EQP\_02 
 
Verify 
equipment 
addition 
failure with 
duplicate ID 
 
Admin is 
logged in, 
equipment ID 
already exists 
 
1. Navigate to 
"Resource 
Management" page. 
2. Select "Add 
Equipment" . 3. Enter 
existing equipment 
ID. 4. Submit form. 
Error message 
appears: 
"Equipment ID 
already exists. " 
Equipment is not 
added. 
 
TC\_TOOL\_0
1 
 
Confirm 
successful 
tool addition 
by admin 
 
Admin is 
logged in with 
valid 
credentials 
 
1. Navigate to 
"Resource 
Management" page. 
2. Select "Add Tool" . 
3. Fill in details (tool 
ID, name). 4. Submit 
form. 
Tool is added 
successfully. New 
tool appears with 
status "Available" . 
 
TC\_TOOL\_0
2 
 
Verify tool 
status 
update by 
admin 
 
Admin is 
logged in, tool 
exists in 
system 
 
1. Navigate to 
"Resource 
Management" page. 
2. Select tool by ID. 
3. Update status to 
"In Use" . 4. Submit 
changes 
Tool status updates 
to "In Use" . 
Changes are 
reflected in the 
system 
 
 

\section*{Page 25}
25 | P a g e 
 
 
 
 
 
 
Pickup Request Management | Weerathunga A W T C 
IT23325814 
Test ID Test Case Preconditions Steps Expected 
Result 
     
TC\_00 
 
Successful 
Request 
Submission 
User is logged 
in, database is 
accessible. 
1.Go to the 
"Create Bin" 
page. 
2.Fill in the 
“Pickup 
Request” form. 
3.Click 
"Submit". 
 
Pickup fee 
displayed. 
"Request 
submitted 
successfully" 
shown, 
redirected to 
“My Bin 
Details” page 
with request. 
(Status: 
"Pending") 
TC\_01 
 
Incomplete 
Form 
Submission 
User is logged 
in. 
1.Go to the 
"Create Bin" 
page. 
2.Leave 
"Address" 
blank, fill 
others. 
3.Click 
"Submit". 
"Please fill in 
this field" 
message 
appears, form 
remains, no 
submission 
occurs. 
TC\_02 
 
Update Pickup 
Request 
A pickup 
request with 
Bin ID "0001" 
exists, user is 
logged in. 
1.Go to the "My 
Bin Details" 
page. 
2.Find request 
with Bin ID 
"0001" . 
3.Click "Edit" . 
A "Pickup 
request 
updated 
successfully" 
message 
appears, 
updated details 

\section*{Page 26}
26 | P a g e 
 
4.Change waste 
type to "Plastic, 
Glass" and 
preferred date 
to 
"03/05/2025" . 
5.Click 
"Submit" . 
Pickup fee 
updated. 
 
visible on My 
Bin Details 
page. 
 
TC\_03 Delete Pickup 
Request 
A pickup 
request with 
Bin ID "0001" 
exists, user is 
logged in. 
1.Go to the "My 
Bin Details" 
page. 
2.Find request 
with Bin ID 
"0001" . 
3.Click 
"Delete" . 
4.Confirm 
deletion. 
"Pickup request 
deleted 
successfully" 
message 
appears, 
request no 
longer visible 
on My Pickup 
Requests page. 
TC\_04 
 
Admin Status 
Update 
Admin is logged 
in, a pickup 
request with 
Bin ID "0001" 
exists. 
1.Go to the 
"Pickup 
Requests" 
page. 
2.Find request 
with Bin ID 
"0001" . 
3.Click " Status" 
dropdown list. 
4.Set status to 
"On Progress" . 
 
"Status 
updated 
successfully" 
message 
appears, status 
updated to "On 
Progress" on 
Pickup 
Requests page, 
user sees 
updated status 
on My Pickup 
Requests page. 
TC\_05 
 
Admin Send 
Confirmation 
Email  
Admin is logged 
in, a pickup 
request with 
Bin ID "0001" 
exists. 
1.Go to the 
"Pickup 
Requests" 
page. 
2.Find request 
with Bin ID 
"0001" . 
3.Click "Send 
Mail" . 
"Email sent 
successfully" 
message 
appears, user 
receives a 
confirmation 
email with 
request details. 

\section*{Page 27}
27 | P a g e 
 
TC\_06 Payment 
Process 
A pickup 
request with 
Bin ID "0001" 
exists with 
status 
"Pending" , user 
is logged in. 
Go to the "My 
Bin Details" 
page. 
Find request 
with Bin ID 
"0001" . 
Click "Pay 
Now" . 
Enter payment 
details. 
Submit 
payment. 
A "Payment 
successful" 
message 
appears, 
request status 
updated to "On 
Progress" , user 
receives a 
payment 
confirmation 
email. 
 
9.Functions 
 
1.User/Staff Management 
The User/Staff Management in the "SmartBin" Waste Management System plays a pivotal 
role in providing secure access, role-based operations and efficient manpower 
management. The feature is developed with the aim of providing a central point for users or 
staff registration, performance monitoring and customer interaction to enable easy 
operation of the systems and service delivery. 
 
The system ensures safe registration of users via the ability of customers to register via 
name ,email ,password. Customers, employees and administrators can all perform safe 
login using credentials. The system also offers Multi-Factor Authentication (MFA) feature as 
optional, in which the users have an option to add an extra layer of security to their 
account. Under the Forgotten Password scenario, the users can utilize password recovery 
facility via email to access again. 
 
 

\section*{Page 28}
28 | P a g e 
 
All the users are allowed to control their profiles, modifying or removing the existing data 
such as name, contact details. The administrator also has the authority of controlling the 
role from where he/she can provide suitable access levels to various users. 
 
For the workers, the system includes a task and schedule preview to which they have been 
assigned in which they get to view their daily tasks. Administrators can handle detailed 
worker profiles, performances, and abilities. The system also includes an advance 
electronic recording of attendance whereby workers can clock in and out, thereby 
recording working hours accordingly. 
 
Also, there is a User/Staff Management module with a complaint and feedback facility for 
quality-of-service improvement. Customer as well as Staff members can register 
complaints or feedback through the system specified form, while the Administrator can 
view, track, assign and update status of complaints or feedback. In "SmartBin" the Garbage 
Management System Administrator has complete control of user data, with visibility of a 
list of all registered users and staff for easy management. Administrators also can obtain 
reports on topics like user activity, staff performance and complaints. 
 
The User/Staff Management module is interfaced with all the other modules with each user 
having individual login provided for them. This also interferes with the financial 
Management to receive the salary plans drawn up by the Financial Manager. 
 
Completed Work Work in Progress Work to be Completed 
- Included backend User 
and Staff Mongoose 
Schemas (basic fields). 
- Incorporate Multi-Factor 
Authentication (MFA) logic 
and UI flow. 
- Add internal 
communication/messaging 
feature among 
staff/admin/users if needed 
by user stories. 
- Developed frontend UI 
components for Login, 
Registration, and basic 
Profile View. 
- Refining role assignment 
logic during 
registration/admin update. 
- Complete and refine UI for 
all user/staff/admin 
dashboards and 
management pages. 
- Created backend API 
endpoints for user 
registration (with hashing). 
- Added Attendance 
Mongoose Schema. 
- Implement password 
reset, MFA, file upload, and 
performance calculation on 
the frontend. 

\section*{Page 29}
29 | P a g e 
 
- Backend implementation 
of update user profile data 
(contact, basic details). 
- Developing frontend UI for 
staff Clock-in/Clock-out 
functionality. 
 
- Password Recovery 
feature implemented (token 
generation, email sending, 
password reset form). 
- Develop backend logic 
and UI for staff document 
upload, storage, and 
verification (e.g., 
certifications). 
 
- Developed backend API 
endpoints for staff Clock-in 
and Clock-out. 
- Develop calculation logic 
for displaying total worked 
hours from attendance 
records. 
 
- Added Complaint 
Mongoose Schema 
(submitter, description, 
initial status). 
- Develop backend logic for 
automatic 
calculation/aggregation of 
Staff Performance KPIs 
 
 
 
 
Database Schema 
 

\section*{Page 30}
30 | P a g e 
 
 
 
 
 
 
 
 
 
 


\section*{Page 31}
31 | P a g e 
 
 


\section*{Page 32}
32 | P a g e 
 
 


\section*{Page 33}
33 | P a g e 
 
 


\section*{Page 34}
34 | P a g e 
 
 
const performanceSchema = new mongoose.Schema(\{ 
  staff: \{ 
    type: mongoose.Schema.Types.ObjectId, 
    ref: 'User', 
    required: true 
  \}, 
  reviewPeriod: \{ 
    startDate: \{ 
      type: Date, 
      required: true 
    \}, 
    endDate: \{ 
      type: Date, 
      required: true 
    \} 
  \}, 
  metrics: \{ 
    productivity: \{ 
      type: Number, 
      min: 0, 
      max: 10, 
      default: 0 
    \}, 
    quality: \{ 
      type: Number, 
      min: 0, 
      max: 10, 
      default: 0 
    \}, 
    reliability: \{ 
      type: Number, 
      min: 0, 
      max: 10, 
      default: 0 
    \}, 
    communication: \{ 
      type: Number, 
      min: 0, 
      max: 10, 
      default: 0 
    \}, 
    initiative: \{ 
      type: Number, 
      min: 0, 

\section*{Page 35}
35 | P a g e 
 
      max: 10, 
      default: 0 
    \} 
  \}, 
  overallRating: \{ 
    type: Number, 
    min: 0, 
    max: 10, 
    default: 0 
  \}, 
  feedback: \{ 
    type: String 
  \}, 
  goals: [String], 
  reviewer: \{ 
    type: mongoose.Schema.Types.ObjectId, 
    ref: 'User', 
    required: true 
  \}, 
  createdAt: \{ 
    type: Date, 
    default: Date.now 
  \}, 
  updatedAt: \{ 
    type: Date, 
    default: Date.now 
  \} 
\}); 
 
 

\section*{Page 36}
36 | P a g e 
 
Database Operations 
 


\section*{Page 37}
37 | P a g e 
 
 


\section*{Page 38}
38 | P a g e 
 
 


\section*{Page 39}
39 | P a g e 
 
Algorithms 
 
Step 1.Start 
Step 2. Access to the “SmartBin” web application 
Step 3. Login to the system 
  If credentials are incorrect: Display the error message  
 If correct credentials: 
  If Administrator: Proceed to step 4 
  If Customer or Recycler: Proceed to step 5 
  If Staff :Proceed to Step 6 
 
Step 4: Administrator Dashboard 
1.  
 
 
 
 
 
 
 
Pseudocode 
FUNCTION LoginUser(email, password) 
    // Attempt to find the user by email in the database 
    user = Database.FindUserByEmail(email) 
 
    // Check if user exists 

\section*{Page 40}
40 | P a g e 
 
    IF user IS NULL THEN 
        RETURN "Error: Invalid Credentials" 
    END IF 
 
    // Compare the provided password with the stored hash 
    isPasswordCorrect = Security.ComparePasswordHash(password, 
user.storedPasswordHash) 
 
    IF isPasswordCorrect IS FALSE THEN 
        RETURN "Error: Invalid Credentials" 
    END IF 
 
    // Generate an authentication token (e.g., JWT) 
    authToken = Authentication.GenerateToken(user.id, user.role) 
 
    // Return success status, token, and user role 
    RETURN \{ status: "Success" , token: authToken, role: user.role \} 
 
END FUNCTION 
 
FUNCTION RegisterUser(name, email, password, role) 
    // Validate input data (e.g., email format, password strength) 
    IF IsValid(name, email, password) IS FALSE THEN 
        RETURN "Error: Invalid input data" 
    END IF 
 

\section*{Page 41}
41 | P a g e 
 
    // Check if a user with the given email already exists 
    existingUser = Database.FindUserByEmail(email) 
    IF existingUser IS NOT NULL THEN 
        RETURN "Error: Email already registered" 
    END IF 
 
    // Hash the password securely 
    hashedPassword = Security.HashPassword(password) 
 
    // Create new user data object 
    newUser = \{ 
        name: name, 
        email: email, 
        password: hashedPassword, 
        role: role, // Assign role (e.g., 'Customer' , 'Staff') 
        createdAt: CurrentDateTime() 
    \} 
 
    // Save the new user to the database 
    result = Database.SaveUser(newUser) 
 
    IF result IS "Success" THEN 
        RETURN "Success: User registered successfully" 
    ELSE 
        RETURN "Error: Could not register user" 
    END IF 

\section*{Page 42}
42 | P a g e 
 
 
END FUNCTION 
 
FUNCTION StaffClockIn(staffId) 
    // Check if staff is already clocked in today (optional, depends on rules) 
    // existingRecord = Database.FindTodaysAttendance(staffId) 
    // IF existingRecord IS NOT NULL AND existingRecord.clockOutTime IS NULL THEN 
    //   RETURN "Error: Already clocked in" 
    // END IF 
 
    // Create attendance record 
    newAttendance = \{ 
        staff: staffId, 
        checkInTime: CurrentDateTime(), 
        status: "Present" // Or determine based on time 
        // date: CurrentDate() // If date is stored separately 
    \} 
 
    // Save record to database 
    result = Database.SaveAttendance(newAttendance) 
 
    IF result IS "Success" THEN 
        RETURN "Success: Clock-in recorded" 
    ELSE 
        RETURN "Error: Could not record clock-in" 
    END IF 

\section*{Page 43}
43 | P a g e 
 
 
END FUNCTION 
 
 
FUNCTION StaffClockOut(staffId) 
    // Find the latest open attendance record for the staff member today 
    attendanceRecord = Database.FindOpenAttendanceRecord(staffId) // Find record with 
no clockOutTime 
 
    IF attendanceRecord IS NULL THEN 
        RETURN "Error: No active clock-in record found to clock-out from" 
    END IF 
 
    // Update the record with clock-out time 
    attendanceRecord.clockOutTime = CurrentDateTime() 
    // Optional: Calculate total hours 
    // attendanceRecord.totalHours = CalculateDuration(attendanceRecord.checkInTime, 
attendanceRecord.clockOutTime) 
    attendanceRecord.status = "Completed" // Or similar 
 
    // Save the updated record 
    result = Database.UpdateAttendance(attendanceRecord) 
 
    IF result IS "Success" THEN 
        RETURN "Success: Clock-out recorded" 
    ELSE 
        RETURN "Error: Could not record clock-out" 

\section*{Page 44}
44 | P a g e 
 
    END IF 
 
END FUNCTION 
 
Flow Chart (Activity Diagram) 
 
User Making a complaint 
 
 
 
 
 
 
 
 

\section*{Page 45}
45 | P a g e 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 


\section*{Page 46}
46 | P a g e 
 
 
 
2. Financial Management 
 
Financial Management Module of “SmartBin” Garbage Management System plays a vital 
part in ensuring proper financial resource utilization, tracking, and allocation. The module 
has been particularly designed to provide a central platform for the management of 
subscription plans, pay plans of employees, and financial transactions in the interest of 
ensuring smooth financial operation within the system. 
 
Subscription Plan Management is an important sub-feature of the Financial Management 
System. It allows the Financial Manager to create, edit, and administer multiple 
subscription plans for clients. The plans enable clients to subscribe to waste collection 
services based on their requirements, generating a recurring revenue stream for the 
company. The Financial Manager is also able to create reports for clients subscribed to 
different plans on the pricing page. The reports can also be filtered based on a particular 
subscription plan if needed. 
 
While creating Salary Plans, the Financial Manager can specify different salary plans for 
different job positions. The admin would then apply such pre-specified salary plans to 
determine the monthly salary of employees. In addition, the Financial Manager would be 
able to specify monthly budget plans for the trash system. 
 
The Financial Management Module is integrated with the Staff Management System, and 
through such integration, the Financial Manager can login and conduct financial operations 
effortlessly. It is integrated with the Recycling and Pickup Request Management System for 
customer payment as well. Payment notice or bill notice is dispatched by the Financial 
Manager to the customers. 
 
Moreover, the Financial Manager can also budget and facilitate renewal funds, such as car 
and tool upkeep, to help make the garbage collection system effective and sustainable.  
 

\section*{Page 47}
47 | P a g e 
 
 
Completed Work Work in progress Work to be Completed 
Successfully implement the 
Subscription Plans 
Management with 
searching feature base on 
the subscription plan name 
Creating the Pricing Page 
the customers can choose 
the suitable subscription 
plan for them 
Implement the Budget 
Allocation section that the 
Financial Manager can 
Make Monthly budget 
efficiently. 
Implement the Salary plan 
creating form with read, 
delete and updating 
features 
Create the dashboard for 
the Financial Manager 
Implement the Payment 
section that the Financial 
Manager can view the 
customers payment status  
Implement the Notification 
system so that the 
customers get their 
payment status through 
this. 
 
 
 
Database Schema 
 
Subscription Plan 

\section*{Page 48}
48 | P a g e 
 
    
 
 
 Salary Plan 
 


\section*{Page 49}
49 | P a g e 
 
 
 
 
 
 


\section*{Page 50}
50 | P a g e 
 
Algorithms 
 
Step 1.Start 
Step 2. Access to the “SmartBin” web application 
Step 3. Login to the system 
  If credentials are incorrect: Display the error message  
 If correct credentials: 
  If Financial Manager: Proceed to step 4 
  If Customer or Recycler: Proceed to step 5 
Step 4.Financial Manager’s Dashboard: 
1. Select “Subscription Plans” 
  If select “Add New Plan”: Complete and submit the form 
   If there are errors, display message and retry 
   If Successful, Add the plan to the view table 
  If select “update”: Make the changers and submit  
   If there are errors, display message and retry 
   If Successful, make the Changers  
2. Select “Salary Plan” 
  If select “Add New Plan”: Complete and submit the form 
   If there are errors, display message and retry 
   If Successful, Add the plan to the view table 
  If select “update”: Make the changers and submit  
   If there are errors, display message and retry 
   If Successful, make the Changers  
3. Select “Budget Allocation” 
  Make Budget Plan: Complete and get the document 

\section*{Page 51}
51 | P a g e 
 
   If there are errors, display message and retry 
   If Successful, display successful message 
 Select “Payment” 
  View the Customer payment detail 
   If Payment is not done yet, generate notification to remind payment 
  Generate Customer payment Document 
Step 5.User’s Dashboard 
1. Select “My Payment” 
  If have payment to complete: Complete  
   If there are errors, display message and retry 
   If Successful, display “Payment successful” 
Step 6 . Logout 
Step 7. End 
 
 
Pseudocode 
 
BEGIN 
 Step 1: Start the application 
 Step 2: Access SmartBin web application 
 Step 3: Authentication User 
  AUTHENTICATE(Email, Password) 
  IF credentials are incorrect THEN 
   DISPLAY “Email and Password incorrect” 
RETURN Step 3 
  ELSE  

\section*{Page 52}
52 | P a g e 
 
   IF user\_role =”Financial\_Manager” THEN 
    DISPLAY “Access Granted” 
    GO TO Step 4 
   ELSE IF user-role = “Customer” OR “Recycler” 
    DISPLAY “Access Granted” 
    GO TO Step 5 
   ELSE  
    DISPLAY “Access Denied” 
    EXIT 
   END IF 
 Step 4:DISPLAY “Welcome Financial Manager Dashboard” 
  INPUT choice 
  //Subscription Plan Management 
  IF choice = “Subscription Plan” THEN 
   DISPLAY “1.Add New   2. View   3.Update   4.Delete” 
   INPUT sub\_choice 
   IF sub\_choice = 1 THEN 
INPUT name, price, monthlyLimit, wastetypes, 
CustomTruckformonth, Otherfeatures 
ADD new\_plan() 
   ELSE IF sub\_choice = 2 THEN 
    GENERATE subscription\_report() 
   ELSE IF sub\_choice = 3 THEN 
    INPUT updated\_details 
    UPDATE subscription\_plan(name,updated\_details) 
   ELSE IF sub\_choice = 4 THEN 

\section*{Page 53}
53 | P a g e 
 
    DELETE subscription\_plan() 
   END IF 
  END IF 
   
  //Salary Plan  
  IF choice = “Salary Plan” THEN 
   DISPLAY “1.Add New   2. View   3.Update   4.Delete” 
   INPUT sub\_choice 
   IF sub\_choice = 1 THEN 
INPUT name, basicSalary, bonusPerHour, 
DeductionPercentage 
ADD new\_plan() 
   ELSE IF sub\_choice = 2 THEN 
    GENERATE salary\_report() 
   ELSE IF sub\_choice = 3 THEN 
    INPUT updated\_details 
    UPDATE salary\_plan(name,updated\_details) 
   ELSE IF sub\_choice = 4 THEN 
    DELETE salary\_plan() 
   END IF 
  END IF 
 
  //Budget Allocation 
  IF choice = “Budget Allocation” THEN 
   DISPLAY “Enter Expense Details” 
   INPUT expense\_type, amount, category 

\section*{Page 54}
54 | P a g e 
 
   RECORD expense() 
   GENERATE expense\_report() 
  END IF 
 
  //Payment 
  IF choice = “Payment” THEN 
   GET customer\_payments 
   FOR EACH payment IN cuatomer\_payment DO 
    DISPLAY customer\_id, amount\_due, payment\_status 
    IF payment\_status = “Pending” THEN 
     GENERATE payment\_notification  
     DISPLAY “notification send to customer” 
    END IF 
   END FOR 
   GENERATE payment\_report() 
  END IF 
 Step 5: DISPLAY “Welcome to Customer dashboard” 
  INPUT choice 
  IF choice = “My Payment” THEN 
   GET pending\_payment 
   IF pending\_payment EXISTS THEN 
    DISPLAY pending\_payment, amount, due\_date 
    WHILE payment\_status != “Successful” DO 
     PROCESS payment  
     IF payment\_status = “error” THEN 
      DISPLAY “Error” 

\section*{Page 55}
55 | P a g e 
 
     ELSE 
      DISPLAY “Payment Successful” 
      UPDATE payment\_status 
      EXIT WHILE 
     END IF 
    END WHILE 
   ELSE 
    DISPLAY “No pending payment “ 
   ENDIF 
  ELSE 
   DISPLAY “Invalid” 
  END IF 
 
 Step 6:DISPLAY “Logout Successful” 
   END 
    
   
 
Flow chart(Activity Diagram) 
 
Budget Allocation  
 
 
 
   
 

\section*{Page 56}
56 | P a g e 
 
  
     
 
  
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 


\section*{Page 57}
57 | P a g e 
 
 
 
3. Recycling Management 
The Recycling Management Module of the "SmartBin" Trash Management System is one of 
the subsystems in the system that is designed to make the recycling of trash easier and 
facilitate seamless interactions between recyclers and the system. The module is designed 
for entities and organizations ready to buy trash for recycling and offers an effective portal 
for submission of recycling requests, processing of recycling requests, and tracking of 
recycling requests while offering seamless administrative control. 
  
One of the most important features of the Recycling Management Module is the Garbage 
Recycle Request System. The recycler may log in to the system and choose the "Garbage 
Recycle" option and view the request form. The form asks for mandatory personal details 
and gives the option to choose the desired type of waste (paper, glass, plastic, organic) 
Depending on the type and quantity of waste selected, the system calculates 
automatically the payment to be made to the recycler. On submission, a form validation is 
done; an empty or invalid field invokes an error message prompting the recycler to fill in the 
corresponding field prior to resubmission. Upon successfully submitting, the requests are 
stored and recoverable under the My Order page where the recyclers are able to view 
extensive request information like the type of waste, quantity, and pay. 
  
The module provides request management functionality to recyclers as well. On the My 
Order page, the recyclers can delete or update their requests with a simple "Update" and 
"Delete" buttons. It is very easy for them to modify at any point prior to admin approval. All 
requests are first "Pending, " so the recyclers know it's in progress until the admin comes 
into the picture. 
  
Administratively, the Recycling Request Management function allows the admin to track all 
incoming requests on the Recycling Request page. Admins can view request details, 
cancel unwanted submissions, and change the status of all requests to "Approved" or 
"Rejected. " After changing the status, the update is visible to recyclers on their My Order 
page, with transparency and real-time communication between users and the system. 
  

\section*{Page 58}
58 | P a g e 
 
This module combines with other SmartBin functions, including login and tracking, to allow 
buying trash for recycling easily and quickly. It saves time by automating cost calculations, 
reduces errors by including error checks, and encourages recycling by making the process 
simple and easy to navigate. 
Completed Work Work in progress Work to be Completed 
• Successfully 
implemented the 
Garbage Recycle 
request form with 
waste type selection 
and automatic 
payment 
calculation. 
Testing the request form to 
ensure error messages are 
clear and calculations are 
accurate. 
 
Implement the payment 
section so recyclers can 
pay after approval 
 
• Created the My 
Order page where 
recyclers can view, 
update, and delete 
their requests with a 
"Pending" status. 
 
Creating the UI for view 
payment details 
Create the payment status 
view for admins to check 
recycler payments. 
 
• Implemented the 
Recycling Request 
page for admins to 
view, delete, and 
update request 
statuses to 
"Approved" or 
"Rejected. " 
 
 Add a confirmation email 
system for recyclers once 
payments are completed. 
 
 
• Innovative Enhancements of the Recycling Request Management function: 
Once the request is submitted and payment is made successfully, the system will send an 
email to the patient's email address confirming the payment and providing the 
appointment details. This feature will be implemented using EmailJS, ensuring the 
efficiency and transparency of the system. 
• SQL Queries used : Not applicable since we have used the MERN stack for development.  
(Screenshots of the mongoDB records for this component are attached below) 
 

\section*{Page 59}
59 | P a g e 
 
 
 
 

\section*{Page 60}
60 | P a g e 
 
 
 


\section*{Page 61}
61 | P a g e 
 
• Flow Charts:    
 
 
 
 


\section*{Page 62}
62 | P a g e 
 
                                 
 


\section*{Page 63}
63 | P a g e 
 
• Database Schema 
   
     
     
 
 
 
 
 
 
• Recycling Management Module Pseudocode 
 


\section*{Page 64}
64 | P a g e 
 
FUNCTION SubmitRecycleRequest 
    DISPLAY form with fields 
    INPUT user fills form 
    CALCULATE paymentAmount = getUnitAmount(wasteCategory) * quantity 
    DISPLAY paymentAmount on form 
    IF all fields are filled AND valid THEN 
        SUBMIT form to database 
        SAVE request with status = "Pending" 
        DISPLAY "Request submitted successfully" 
    ELSE 
        DISPLAY "Error: Please fill all fields correctly" 
        ALLOW user to edit and resubmit 
    END IF 
END FUNCTION 
------------------------------------------------------------------------ 
 
FUNCTION MyOrderPage 
    DISPLAY list of user’s submitted requests 
    FOR each request DO 
        SHOW details of fields 
        PROVIDE buttons: "Update" , "Delete" 
    END FOR 
    IF user clicks "Update" THEN 
        ALLOW editing of wasteCategory, quantity 
        RECALCULATE paymentAmount 
        SAVE updated request 

\section*{Page 65}
65 | P a g e 
 
    END IF 
    IF user clicks "Delete" THEN 
        REMOVE request from database 
        DISPLAY "Request deleted" 
    END IF 
END FUNCTION 
------------------------------------------------------------------------ 
FUNCTION RecyclingRequestPage 
    DISPLAY list of all recycler requests 
    FOR each request DO 
        SHOW details of fields 
        PROVIDE buttons: "Delete" , "Update Status" 
    END FOR 
    IF admin clicks "Delete" THEN 
        REMOVE request from database 
        DISPLAY "Request deleted" 
    END IF 
    IF admin clicks "Update Status" THEN 
        SET status = "Approved" OR "Rejected" 
        SAVE updated status 
        NOTIFY recycler (update visible on MyOrderPage) 
    END IF 
END FUNCTION 
------------------------------------------------------------------------ 
// Payment Process (Not Yet Implemented) 
FUNCTION MakePayment 

\section*{Page 66}
66 | P a g e 
 
    IF request.status = "Approved" THEN 
        DISPLAY payment form 
        INPUT payment details 
        SUBMIT payment to financial system 
        SAVE payment status in database 
        DISPLAY "Payment successful" 
    ELSE 
        DISPLAY "Request not approved yet" 
    END IF 
END FUNCTION 
------------------------------------------------------------------------ 
// Payment Process Admin SIde (Not Yet Implemented) 
FUNCTION AdminViewPayment 
    DISPLAY list of payments for approved requests 
    SHOW payment details: recycler, amount, date 
    SEND confirmation email to recycler 
END FUNCTION 
 
• Algorithm: SubmitRecycleRequest 
 
ALGORITHM SubmitRecycleRequest 
INPUT: personalInfo, wasteCategory (e.g., paper, glass, plastic, organic), quantity 
OUTPUT: Submitted request or error message 
  
1. DISPLAY form with fields: personalInfo, wasteCategory, quantity 
2. GET user input for all fields 

\section*{Page 67}
67 | P a g e 
 
3. SET paymentAmount = getUnitAmount(wasteCategory) * quantity 
4. DISPLAY paymentAmount on form 
5. IF personalInfo is not empty AND wasteCategory is valid AND quantity > 0 THEN 
    6. SUBMIT form data to database 
    7. SAVE request with personalInfo, wasteCategory, quantity, paymentAmount, status = 
"Pending" 
    8. DISPLAY "Request submitted successfully" 
9. ELSE 
    10. DISPLAY "Error: Please fill all fields correctly" 
    11. ALLOW user to edit fields 
    12. RETURN to step 2 for resubmission 
13. END IF 
END ALGORITHM 
 
• Algorithm: MyOrderPage 
 
ALGORITHM MyOrderPage 
INPUT: None (uses logged-in user’s data) 
OUTPUT: Updated or deleted request list 
  
1. FETCH user’s submitted requests from database 
2. DISPLAY list of requests 
3. FOR each request DO 
    4. SHOW details: wasteCategory, quantity, paymentAmount, status 
    5. PROVIDE buttons: "Update" , "Delete" 
6. END FOR 
7. IF user clicks "Update" THEN 

\section*{Page 68}
68 | P a g e 
 
    8. ALLOW editing of wasteCategory, quantity 
    9. GET updated input from user 
    10. SET paymentAmount = getUnitAmount(wasteCategory) * quantity 
    11. SAVE updated request in database 
    12. DISPLAY "Request updated" 
13. END IF 
14. IF user clicks "Delete" THEN 
    15. REMOVE request from database 
    16. DISPLAY "Request deleted" 
17. END IF 
18. REFRESH list of requests 
END ALGORITHM 
 
• Algorithm: RecyclingRequestPage 
 
ALGORITHM RecyclingRequestPage 
INPUT: None (uses admin access) 
OUTPUT: Updated or deleted request list 
  
1. FETCH all recycler requests from database 
2. DISPLAY list of requests 
3. FOR each request DO 
    4. SHOW details: personalInfo, wasteCategory, quantity, paymentAmount, status 
    5. PROVIDE buttons: "Delete" , "Update Status" 
6. END FOR 
7. IF admin clicks "Delete" THEN 

\section*{Page 69}
69 | P a g e 
 
    8. REMOVE request from database 
    9. DISPLAY "Request deleted" 
10. END IF 
11. IF admin clicks "Update Status" THEN 
    12. PROMPT admin to choose "Approved" or "Rejected" 
    13. SET status = chosen value 
    14. SAVE updated status in database 
    15. NOTIFY recycler by updating MyOrderPage 
    16. DISPLAY "Status updated" 
17. END IF 
18. REFRESH list of requests 
END ALGORITHM 
 
• Algorithm: MakePayment (Not Yet Implemented) 
 
ALGORITHM MakePayment 
INPUT: request (with status) 
OUTPUT: Payment submission or error message 
  
1. IF request.status = "Approved" THEN 
    2. DISPLAY payment form 
    3. GET payment details from user 
    4. SUBMIT payment details to financial system 
    5. SAVE payment status in database 
    6. DISPLAY "Payment successful" 
7. ELSE 
    8. DISPLAY "Request not approved yet" 

\section*{Page 70}
70 | P a g e 
 
9. END IF 
END ALGORITHM 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
4.Schedule/ Resource Management 
 
The Schedule/Resource Management feature in the "SmartBin" Waste Management 
System is a critical component designed to streamline the planning, execution, and 
oversight of daily collection operations and resource allocation. This feature aims to 
provide a centralized platform for scheduling routes, managing vehicles and equipment, 

\section*{Page 71}
71 | P a g e 
 
and enabling efficient coordination between administrators and drivers to ensure seamless 
service delivery. 
  
The system allows administrators and schedulers to manually create basic collection 
routes by assigning specific areas and customers, ensuring operational flexibility and 
precision in planning. Drivers (staff) can securely access their assigned routes and 
customer lists for the day through a user-friendly interface, empowering them to carry out 
their tasks effectively. This visibility into daily schedules enhances accountability and 
productivity across the workforce. 
  
For resource oversight, the system enables administrators to register vehicles and assign 
basic statuses such as "Active" or "Maintenance, " facilitating fleet management and 
ensuring operational readiness. Additionally, administrators can add new equipment and 
tools, managing their availability to support the workforce efficiently. A map view feature 
provides administrators with basic vehicle location tracking, offering real-time insights into 
fleet activity for improved decision-making. 
  
Drivers benefit from an interactive route management tool that allows them to mark 
pickups as completed directly on their route list, keeping progress updated and providing 
administrators with accurate records of completed tasks. This feature fosters a dynamic 
feedback loop between field staff and management, ensuring transparency and 
operational efficiency. 
  
The Schedule/Resource Management module also integrates advanced functionalities to 
support long-term planning and resource optimization. Administrators have full control 
over route assignments, vehicle statuses, and equipment inventories, with the ability to 
monitor and adjust resources as needed. The system can generate reports on route 
efficiency, vehicle utilization, and driver performance, providing actionable insights for 
continuous improvement. 
  
Designed to interface seamlessly with other system modules, such as User/Staff 
Management and Financial Management, the Schedule/Resource Management feature 
ensures that scheduling data aligns with staff availability and budget considerations. Each 

\section*{Page 72}
72 | P a g e 
 
user, whether an administrator or driver, accesses the system through individual login 
credentials, maintaining security and role-based access. This interconnected design 
supports a cohesive waste management ecosystem, where resource allocation and 
scheduling contribute directly to operational success and customer satisfaction 
 
 
Completed Work Work in progress Work to be Completed 
Successfully implemented 
the route creation 
functionality for admins 
with form validation 
 
Creating the map view for 
admins to track vehicle 
locations 
 
Enhance the scheduling 
system with conflict 
detection 
 
Implemented the route 
viewing feature for drivers 
with search functionality 
 
 Implement a notification 
system for drivers to receive 
real-time route updates 
 
Successfully added the 
truck management feature 
with CRUD operations 
 
  
 
Database Schema 
 
Equipments  

\section*{Page 73}
73 | P a g e 
 
 
 
 
 
 
 
 
Tools 
 


\section*{Page 74}
74 | P a g e 
 
 
 
 
 
 
 
 
 
 
 
 
 


\section*{Page 75}
75 | P a g e 
 
Trucks 
 
 
 
 
 
 
 


\section*{Page 76}
76 | P a g e 
 
Schedule 
 
 
Algorithms 
 
For Scheduling 
Step 1. Start 
  
Step 2. Access the “SmartBin” web application 
  
Step 3. Login to the system 
    If credentials are incorrect: Display "Invalid credentials" message 
    If correct credentials and user is Admin: Proceed to Step 4 
  
Step 4. Admin Dashboard 


\section*{Page 77}
77 | P a g e 
 
    Select “Schedule Management” 
    Choose “Create New Route” 
    Enter route details (areas/customers, truck number, date, time) 
    Submit the form 
    If there are errors (e.g., invalid truck, past date): Display "Error in route creation" and retry 
    If successful: 
        Generate unique schedule number 
        Save route to system 
        Update truck availability to "In Use" 
        Display "Route created successfully" 
  
Step 5. Logout 
  
Step 6. End 
 
 
For equipment/tools 
 
 
Step 1. Start 
  
Step 2. Access the “SmartBin” web application 
  
Step 3. Login to the system 
    If credentials are incorrect: Display "Invalid credentials" message 
    If correct credentials and user is Admin: Proceed to Step 4 
  
Step 4. Admin Dashboard 

\section*{Page 78}
78 | P a g e 
 
    Select “Resource Management” 
    Choose “Add New Equipment” or “Add New Tool” 
    Enter resource details (ID, name, description) 
    Submit the form 
    If there are errors (e.g., duplicate ID): Display "Error adding resource" and retry 
    If successful: 
        For Equipment: Set status to "Operational" 
        For Tool: Set status to "Available" 
        Save resource to system 
        Display "Resource added successfully" 
  
    Choose “Update Availability” 
    Select resource by ID 
    Update status (e.g., "Maintenance" for Equipment, "In Use" for Tool) 
    Submit changes 
    If there are errors: Display "Error updating status" and retry 
    If successful: Display "Resource availability updated" 
  
Step 5. Logout 
  
Step 6. End 
 
 
 

\section*{Page 79}
79 | P a g e 
 
Pseudocode 
 
 
 
\\Schedule management 
 
 
FUNCTION CreateCollectionRoute(adminId, areas, truckNo, date, time) IF NOT 
isAdmin(adminId) THEN RETURN "Unauthorized access" END IF 
SET scheduleNo = "SCH-" + CURRENT\_TIMESTAMP + RANDOM\_STRING(4) 
 
IF areas IS EMPTY OR NOT isValidTruck(truckNo) OR NOT 
isFutureDate(date, time) THEN 
    RETURN "Invalid input data" 
END IF 
 
SET newSchedule = \{ 
    scheduleNo: scheduleNo, 
    route: areas, 
    truckNo: truckNo, 
    date: date, 
    time: time, 
    status: "Waiting" 
\} 
 
TRY 
    SAVE newSchedule TO ScheduleCollection 
    UPDATE TruckCollection WHERE truckNo = truckNo SET availability = 
"In Use" 
CATCH error 
    RETURN "Failed to create route: " + error 
END TRY 
 
RETURN "Route created successfully" WITH newSchedule 
  
END FUNCTION 

\section*{Page 80}
80 | P a g e 
 
 
 
\\Equipment  manage 
 
 
FUNCTION AddEquipment(adminId, equipmentId, name, description) 
    IF NOT isAdmin(adminId) THEN 
        RETURN "Unauthorized access" 
    END IF 
  
    IF equipmentId IS EMPTY OR name IS EMPTY OR EXISTS IN 
EquipmentCollection(equipmentId) THEN 
        RETURN "Invalid or duplicate equipment data" 
    END IF 
  
    SET newEquipment = \{ 
        equipmentId: equipmentId, 
        name: name, 
        status: "Operational" , 
        description: description OR NULL 
    \} 
  
    TRY 
        SAVE newEquipment TO EquipmentCollection 
    CATCH error 
        RETURN "Failed to add equipment: " + error 
    END TRY 

\section*{Page 81}
81 | P a g e 
 
  
    RETURN "Equipment added successfully" WITH newEquipment 
END FUNCTION 
 
 
\\Tool manage 
 
 
FUNCTION AddTool(adminId, toolId, name, description) 
    IF NOT isAdmin(adminId) THEN 
        RETURN "Unauthorized access" 
    END IF 
  
    IF toolId IS EMPTY OR name IS EMPTY OR EXISTS IN ToolCollection(toolId) THEN 
        RETURN "Invalid or duplicate tool data" 
    END IF 
  
    SET newTool = \{ 
        toolId: toolId, 
        name: name, 
        status: "Available" , 
        description: description OR NULL 
    \} 
  
    TRY 
        SAVE newTool TO ToolCollection 
    CATCH error 
        RETURN "Failed to add tool: " + error 

\section*{Page 82}
82 | P a g e 
 
    END TRY 
  
    RETURN "Tool added successfully" WITH newTool 
END FUNCTION 
 
 
 
 
 
 


\section*{Page 83}
83 | P a g e 
 
 
 
 
 
 
7. Pickup Request Management 
The “Pickup Request Management” module of the "SmartBin" Online Garbage 
Management System is one of the most critical modules of the system which will facilitate 
the request and management process of garbage pickup requests in a highly effective way, 
thus offering a seamless interaction experience between users and the system. This 
module is intended to meet those individuals, families, and companies who are interested 
in sending their trash green and provides a clean entry for sending, monitoring, and 
processing pickup requests and enabling firm administrative control. 
The most outstanding feature of the Pickup Request Management Module is the “Garbage 
Pickup Request System” . The user can log in to the SmartBin system, view the "Pickup 
Request" page, and send the pickup request form. The form provides information such as 
the user's name, phone number, email address, address, type of community (e.g.- 
household or industry), date of preferred pickup and which type of waste to collect (e.g.- 
organic, plastic, paper, or glass). The customers are also allowed to select their pickup 
point on the interactive map that will automatically take the latitude and longitude for 
precise pickup booking. Based on the selected types of waste and address the system will 
auto-calculate the pickup charge, hence transparency of the charges. On submission, the 
form is validated; in case any of the mandatory fields are empty or incorrect input-that is, 
an incorrect format for the email-then the system will raise an error message to correct the 
field and to resubmit. After successful submission, the pickup request is stored in the 
system and is provided on the user's "My Pickup Requests" page where he can view full 
details such as bin ID, waste type, pickup date, location, and calculated amount. 
The module provides full request management to the users at the "My Pickup Requests" 
page. The following are all the users' pickup requests, and they all default to "Pending" 
status to indicate that the request is pending admin approval. Users can delete or update 
their requests with easy "Update" and "Delete" buttons so that they can modify details 
such as the pickup date or waste type before the request is handled by the admin. This 
feature helps users monitor their requests with ease and update whenever needed until the 
request is processed or approved by the admin. 

\section*{Page 84}
84 | P a g e 
 
In the admin end, the “Pickup Request Management” feature enables admins to efficiently 
manage all pickup requests placed via the "Pickup Requests" page. Admins are able to 
view full details for each request, including user details, waste type, address, and preferred 
pickup date. The page groups the requests into three categories for easy handling: “Works 
to be Completed” (Pending requests), “Works in Progress” (On Progress requests) and 
“Completed Works” (Completed requests). The admins can individually update all the 
requests' status manually (e.g.- from "Pending" to "On Progress" or "Completed") using a 
drop-down menu, mark unwanted as cancelled, or even delete them all as and when 
needed. The users are then informed of the update on their "My Pickup Requests" page to 
provide transparency and live connectivity between the user and the system. Besides, 
admins can also automatically send an email to the users through a "Send Mail" button 
sending an email of confirmation with the pickup request details, thank-you message, and 
link to view the pickup schedule. 
The Pickup Request Management Module is integrated into the other SmartBin 
functionalities to create a more unified user experience. It, being a model, contains an 
association with the login mechanism in a way that the admins and the users are given 
secure access. It is also associated with the functionality of mapping (through Leaflet) 
such that customers can input their pickup location in detail, and with the email 
notification function such that auto-generated confirmation emails are sent. Also, the 
system needs to be integrated with a payment gateway to be created in the future so that 
customers can pay the estimated pickup fee online, and the request status will be updated 
accordingly (e.g.- from "Pending" to "On Progress" on payment). 
 
This module simplifies the garbage collection process by auto-processing some of the 
most important steps such as computation of charges and identifying location and 
reducing error through form validation and live status. 
It is an admin and user saving time by single-point management of requests, clear with 
easy-to-follow status and encourages responsible dumping by making the process clear 
and all the people concerned more responsive. By its administrative role, the module 
ensures effective scheduling and processing of pickup orders, thereby qualifying the 
SmartBin system as a viable online waste management system. 
 
 
 
 

\section*{Page 85}
85 | P a g e 
 
 
 
Completed Work Work in progress Work to be Completed 
Successfully implemented 
the Garbage Pickup 
Request Form with 
automatic payment amount 
calculation and validations 
to prevent incomplete or 
invalid submissions. 
Implementing an 
Automated Email 
Notification System to send 
confirmation with waste 
collecting details. 
Plan to Implement a Secure 
and User-Friendly Payment 
Gateway to enable 
transactions after pickup 
request approved. 
Designed user-friendly "My 
Bin Details" and "Pickup 
Request Details" pages 
through which customers 
can view and manage their 
submitted pickup requests 
with full CRUD 
functionality. 
 Plan to generate summary 
reports of completed 
Pickup Requests and admin 
will have the ability to 
download reports in 
formats such as PDF. 
Implemented a dynamic 
Search Feature that allows 
users and administrators to 
search pickup requests 
using various keywords 
  
Designed an admin 
dashboard to display all 
pickup requests submitted 
by customers with data 
retrieved dynamically from 
the database 
  
Implemented a Status 
Update System whereby the 
admin will have the ability 
to update the status of any 
pickup request and admin 
changes will update 
automatically in the 
respective User's "My Bin 
Details" page, which will 
give real-time updates 
  
 
 

\section*{Page 86}
86 | P a g e 
 
 
 
 
 
 
 
 
 
 
• Innovative Enhancements of the Recycling Request Management function: 
Once the pickup request is approved, the system will send an email to the customer’s 
email address confirming the payment and providing the pickup details. This feature will 
be implemented using nodemailer, ensuring efficient communication and transparency in 
the waste pickup process. 
 
• SQL Queries used : Not applicable since we have used the MERN stack for development.  
(Screenshots of the MongoDB records for this component are attached below) 
 
 

\section*{Page 87}
87 | P a g e 
 
 
 
 
 
 
 
 
 
• Database Schema 


\section*{Page 88}
88 | P a g e 
 
 
 
• Pickup Request Management Module Pseudocode 
FUNCTION SubmitPickupRequest 
    DISPLAY form with fields (name, contactNumber, email, community, wasteType, address, 
preferredDate, serviceType, location, pickupFee, status) 
 
    CALCULATE pickupFee = getBaseFee() + (wasteType.length * additionalFeePerType) 
  
    DISPLAY pickupFee on form 
  
    IF all fields are filled AND valid THEN 
        SUBMIT form to database 


\section*{Page 89}
89 | P a g e 
 
        SAVE request with status = "Pending" 
        DISPLAY "Pickup request submitted successfully" 
    ELSE 
        DISPLAY "Error: Please fill all fields correctly" 
        ALLOW user to edit and resubmit 
    END IF 
END FUNCTION 
 
FUNCTION MyPickupRequestsPage 
    DISPLAY list of user’s submitted pickup requests 
  
    FOR each request DO 
        SHOW details of fields (name, contactNumber, email, community, wasteType, address, 
preferredDate, serviceType, location, pickupFee, status) 
        PROVIDE buttons: "Update" , "Delete" 
    END FOR 
  
    IF user clicks "Update" THEN 
        ALLOW editing of wasteType, address, preferredDate, serviceType, location 
        RECALCULATE pickupFee = getBaseFee() + (wasteType.length * additionalFeePerType) 
        SAVE updated request 
        DISPLAY "Pickup request updated" 
    END IF 
  
    IF user clicks "Delete" THEN 
        REMOVE request from database 

\section*{Page 90}
90 | P a g e 
 
        DISPLAY "Pickup request deleted" 
    END IF 
END FUNCTION 
 
FUNCTION PickupRequestsPage 
    DISPLAY list of all pickup requests 
  
    FOR each request DO 
        SHOW details of fields (name, contactNumber, email, community, wasteType, address, 
preferredDate, serviceType, location, pickupFee, status) 
        PROVIDE buttons: "Delete" , "Update Status" 
    END FOR 
  
    IF admin clicks "Delete" THEN 
        REMOVE request from database 
        DISPLAY "Pickup request deleted" 
    END IF 
  
    IF admin clicks "Update Status" THEN 
        SET status = "Pending" OR "On Progress" OR "Completed" OR "Cancelled" 
        SAVE updated status 
        NOTIFY user (update visible on MyPickupRequestsPage) 
        DISPLAY "Status updated" 
    END IF 
END FUNCTION 
 

\section*{Page 91}
91 | P a g e 
 
FUNCTION MakePayment 
    IF request.status = "Pending" THEN 
        DISPLAY payment form 
        INPUT payment details 
        SUBMIT payment to financial system 
        SAVE payment status in database 
        SET request.status = "On Progress" 
        DISPLAY "Payment successful" 
    ELSE 
        DISPLAY "Payment can only be made for Pending requests" 
    END IF 
END FUNCTION 
 
FUNCTION AdminViewPayment 
    DISPLAY list of payments for processed pickup requests 
    SHOW payment details: user, amount, date 
    SEND confirmation email to user 
END FUNCTION 
 
• Algorithms 
 
ALGORITHM SubmitPickupRequest 
INPUT: name, contactNumber, email, community, wasteType, address, preferredDate, 
serviceType, location (lat, lng) 
OUTPUT: Submitted pickup request or error message 
  

\section*{Page 92}
92 | P a g e 
 
1. DISPLAY form with fields: name, contactNumber, email, community, wasteType, 
address, preferredDate, serviceType, location (map) 
2. GET user input for all fields 
3. SET pickupFee = getBaseFee() + (wasteType.length * additionalFeePerType) 
4. DISPLAY pickupFee on form 
5. IF name IS NOT EMPTY AND contactNumber IS NOT EMPTY AND email IS NOT EMPTY 
AND community IS NOT EMPTY AND wasteType IS NOT EMPTY AND address IS NOT EMPTY 
AND preferredDate IS NOT EMPTY AND serviceType IS NOT EMPTY AND location IS VALID 
THEN 
    6. SUBMIT form data to database 
    7. SAVE request with name, contactNumber, email, community, wasteType, address, 
preferredDate, serviceType, location, pickupFee, status = "Pending" 
    8. DISPLAY "Pickup request submitted successfully" 
9. ELSE 
    10. DISPLAY "Error: Please fill all fields correctly" 
    11. ALLOW user to edit fields 
    12. RETURN to step 2 for resubmission 
13. END IF 
END ALGORITHM 
 
ALGORITHM MyPickupRequestsPage 
INPUT: None (uses logged-in user’s data) 
OUTPUT: Updated or deleted request list 
  
1. FETCH user’s submitted pickup requests from database 
2. DISPLAY list of requests 
3. FOR each request DO 

\section*{Page 93}
93 | P a g e 
 
    4. SHOW details: name, contactNumber, email, community, wasteType, address, 
preferredDate, serviceType, location, pickupFee, status 
    5. PROVIDE buttons: "Update" , "Delete" 
6. END FOR 
7. IF user clicks "Update" THEN 
    8. ALLOW editing of wasteType, address, preferredDate, serviceType, location 
    9. GET updated input from user 
    10. SET pickupFee = getBaseFee() + (wasteType.length * additionalFeePerType) 
    11. SAVE updated request in database 
    12. DISPLAY "Pickup request updated" 
13. END IF 
14. IF user clicks "Delete" THEN 
    15. REMOVE request from database 
    16. DISPLAY "Pickup request deleted" 
17. END IF 
18. REFRESH list of requests 
END ALGORITHM 
 
ALGORITHM PickupRequestsPage 
INPUT: None (uses admin access) 
OUTPUT: Updated or deleted request list 
  
1. FETCH all pickup requests from database 
2. DISPLAY list of requests 
3. FOR each request DO 
    4. SHOW details: name, contactNumber, email, community, wasteType, address, 
preferredDate, serviceType, location, pickupFee, status 

\section*{Page 94}
94 | P a g e 
 
    5. PROVIDE buttons: "Delete" , "Update Status" 
6. END FOR 
7. IF admin clicks "Delete" THEN 
    8. REMOVE request from database 
    9. DISPLAY "Pickup request deleted" 
10. END IF 
11. IF admin clicks "Update Status" THEN 
    12. PROMPT admin to choose "Pending" , "On Progress" , "Completed" , "Cancelled" 
    13. SET status = chosen value 
    14. SAVE updated status in database 
    15. NOTIFY user by updating MyPickupRequestsPage 
    16. DISPLAY "Status updated" 
17. END IF 
18. REFRESH list of requests 
END ALGORITHM 
 
ALGORITHM MakePayment 
INPUT: request (with status) 
OUTPUT: Payment submission or error message 
  
1. IF request.status = "Pending" THEN 
    2. DISPLAY payment form 
    3. GET payment details from user 
    4. SUBMIT payment details to financial system 
    5. SAVE payment status in database 
    6. SET request.status = "On Progress" 

\section*{Page 95}
95 | P a g e 
 
    7. DISPLAY "Payment successful" 
8. ELSE 
    9. DISPLAY "Payment can only be made for Pending requests" 
10. END IF 
END ALGORITHM 
 
ALGORITHM AdminViewPayment 
INPUT: None (uses admin access) 
OUTPUT: List of payments 
  
1. FETCH all payments for processed pickup requests from database 
2. DISPLAY list of payments 
3. FOR each payment DO 
    4. SHOW details: user, amount, date 
    5. SEND confirmation email to user 
6. END FOR 
END ALGORITHM 
 
 
 
 
 
 
 
 

\section*{Page 96}
96 | P a g e 
 
 
 


\end{document}
